Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-19 prop_letter.tex
prop_letter.tex Updating...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
However, it is not evident at all that this resource-aware perspective
does not alter the very foundations of quantum mechanics. Indeed taking
such resource bounds into consideration is what founded computer science
as a discipline and has become crucial for understanding the very
nature of computation. Following Feynman~\citep{Feynman1982Simulating},
Landauer~\citep{Landauer1996188}, and others, one might argue that
this resource-bounded perspective is also crucial for understanding
the very nature of physical processes.

In previous work, we analyzed the wave function description of quantum
systems from a resource-bounded perspective. Technically, instead
of postulating that quantum states are rays in a Hilbert space, i.e.,
we instead used special finite fields whose size reflected the available
resources. \ldots{}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
Following Feynman~\citep{Feynman1982Simulating}, Landauer~\citep{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
However, it is not evident at all that this resource-aware perspective
does not alter the very foundations of quantum mechanics.

In conventional quantum theory, when we measure a system described
by a state~$\ket{\phi}$ with respect to an observable~$\mathbf{O}$,
the probability of getting a eigenvalue~$\lambda$ is completely
determined by $\ket{\phi}$ and the eigenspace of $\lambda$, $S_{\lambda}$.
If we denote the projector to $S_{\lambda}$ as $P_{\lambda}$, the
probability of getting $\lambda$ can be computed by the Born rule~$\mu_{\phi}^{\mathrm{\mathrm{B}}}\left(P_{\lambda}\right)=\ip{\phi}{P_{\lambda}\phi}$.
In another word, any state~$\ket{\phi}$ defines a quantum probability
measure~$\mu_{\phi}^{\mathrm{\mathrm{B}}}:\events\rightarrow[0,1]$,
where $\events$ is the set of all projectors in a Hilbert space.
Conversely, given any quantum probability measure~$\mu:\events\rightarrow[0,1]$
which should satisfy:
\begin{itemize}
\item $\mu(\mathbb{0})=0$. 
\item $\mu(\mathbb{1})=1$. 
\item For any projection $P$, $\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$. 
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have $\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)$. 
\end{itemize}
The Gleason's theorem asserts that there exists a unique mixed state~$\rho$
such that $\mu=\mu_{\rho}^{\mathrm{\mathrm{B}}}$ in a Hilbert space
$\Hilb$ of dimension $d\geq3$.

\paragraph{Gleason's Theorem}

\paragraph{The Kochen-Specker Theorem}
